\documentclass{article}
\begin{document}
\title{History Reading Assginment Pages:  PP675-682, 691-707}
\author{Huy Le}
\maketitle
\section{Main points from the Reading}
\begin{itemize}
\item Good neighbor policy:
\item Road to War
\item How American react to the beginning of the war by German and Italian
\item Lend-Lease Act
\item Pearl Harbor
\item D- day
\item Stalingrad
\item Holocaust
\item the begin of racism's ending
\item Mexican, Indians, and Asian during the war
\item Black Segregration during war time
\item Executive Order 8802:
\item An American Dilema
\item Atomic bomb
\item United Nations
\end{itemize}

\section{Mainpoints Explained}
\subsection{Good neighbor policy:}
- United States repudiated the right to intervene military in the internal affairs of Latin American countries.\\
- also lent its support to dictators like Anastasio Somoza in Nicaragua, Rafael Trujillo Molina in the Dominican. \\
- FDR state that Somoza is our son of a bitchhh.\\

\subsection{ Road to War}
- 1931, Japan invade Manchuria, province of China, to expand its military and economic power.\\
- Japanese overran Nanjing, killed 300,000 Chineses.\\
- Adolf Hitler wants to take control over whole Europe, sent troops to occupy Rhineland.\\
- Italian leader Musolini invaded Ethiopia. 
- Roosevelt is alarmed by Hitler aggression.

\subsection{ How American react to the beginning of the war by German and Italian}
- Obsessed with the threat of Communism, some American approve the expansion of German as a counter to Soviet Union.\\
- Henry Ford did business with Nazi Germany throughout the 1930s. \\
- Trade with Japan still going.\\
- Many American of Germany and Italian celebrate on the expansion of their original country even though they didn't like that kind of government.\\
- \textbf{Isolationism:} Ideas of American avoid involving to the war by Netrality Acts that banned the sale of arms to countries at war.\\

\subsection{ Lend-Lease Act}
- Authorize military aid so long as countries promise somehow to return it all after the war.\\
- funneled billions of dollar worth of arms to Britain and China, as well as Soviet Union.\\
- FDR also freeze the Japanese assets in the United States, halting virtually all trade between the countries, including the sale of oil vital to Japan.\\

\subsection{ Pearl Harbor}
- Dec 7, 1941. Japanese planes launched from aricraft carries, bombed the naval base at Pearl Harbor in Hawaii. \\
- 2000 servicemen were killed, 187 aircraft and 18 naval vessels including 8 battle ships had been destroyed\\
- Roosevelt ask Congress to declare war against Japan\\
- 477 Vote yes, 1 said no.\\
- Germany declared wawr on the United States.\\
- America had finally joined the largest war.\\

\subsection{D- day}
- June 6, 1944. 200,000 American British, and Candian soldiers under the commmand of Dwight D. Eisenhower landed in Normandy.\\
- More than a million troops followed them ashore.\\
- German retreat East after the fight\\

\subsection { Stalingrad}
- 1942 German tried to occupy Stalingrad which is a city deep inside Russia. \\
- It was a mistake. \\
- With the help of supply from United States, Russia surrounded Germany and force them to surrender in 1943. \\
- This is the turning point in the war\\

\subsection{ Holocaust}
- Final solution\\
- Mass extermination of undesireable peoples.\\
- Slavs, gypsies, homosexuals, and above all, Jews\\
- 1945, 6 millions Jewish men, women and children had died in Nazi camp.\\

\subsection { the begin of racism's ending}
- horrified by the Nazi way of inborn racial difference, biological scientists abandoned belief in a link among race, culture , and intelligence.\\
- By the war's end, racism and nativism had been stripped of intellectual respectability, at least outside of the South, and were viewed as psychological disorders\\

\subsection { Mexican, Indians, and Asian during the war}
- \textbf{Mexican}: Bracero program agreed to by the Mexican and American Government in 1942. Ten thousands of contract laboreres crossed into the United States to take up jobs as domestic and agricultural workers. Program lasted until 1964, more than 4.5 millions Mexican enter United States under labor contract.\textbf{Zoot suit} police men attacked Mexican-American youth wearing flamboyant clothing on the street of Lost Angeles\\
- \textbf{ Indians: } 250,000 served in the army, including the Navajo code talkers, transmitted message in their complex native language which Japanese can't understand. Iroquois issued their own declaration  of war against the Axis power. 10,000 of Indian left reservation for jobs in industries. Many choose not to return when the war ended.\\
- \textbf{ Asian American }: 50,000 asisan fought in the army, mostly all-Asian units. Since China was the ally in the Pacific war, Congress in 1943 ended decades of complete exclusion by establishing a nationality quota for Chinese immigrants.\\
- \textbf{Japanese } Government potrayed Japanese as rats, dogs, gorillaas, and snakes. FDR issued Executive Order 9066, this ordered the expulsion of all persons of Japanese descent from the West Coast. Authorities put Japanese into internment camps fra from the home. Government ask Japanese to have a loyalty oath. 1988 Congress appologized, and give 20,000 dollar to each surviving victim\\

\subsection{ Black Segregration during war time}
- \textbf{ American is like Nazi Germany in a lot of way}. Red Cross refuse to mix blood from blacks and whites in its blood banks.( discriminate black and white just like the Nazi ideas about race)\\
-\textbf{ Segregration in Army.}Airforce and marines has no black members. Navy accepted baclk only as waiters and cooks. Black soldiers joined non-combat units only.\\
\textbf{GI Bill:} local authorities declined black rights and benefits from GI Bill, only get to use education benefits at segregated colleges, limit job trainning to unskilled work and low-wages service job\\

\subsection{Executive Order 8802:}
- A. Phillip Randolph in July 1941 called for a March on Washington, demanding for access to defense employment, and end to segregation, and a national antilynching law.\\
- Roosevelt issue 8802 which banned discrimination in defense jobs and established a \textbf{Fair employment Practices Commission} FEPC to monitor compliance.\\
- FEPC played an important role in obtaining jobs for black workers in industrial plants and shipyards.\\

\subsection{ An American Dilema}
- A book written  by Swedish social scientist \textbf{ Gunnar Myral:} the boook offer an uncompomising portrait of how deeply racism were entrenched in law, politics, economis, and social behaviors. \\
- He thinks that there would be the redefinition of Negro as a result of the war.\\
- His book got a lot of attetion because the context oif worldwide struggle against Nazi and rising black demands for equality at home.\\
- The book indentifies serious national problem and seemed to offer an alomost painless path to peaceful changes, in which the government will take the lead in outlawing discrimination.\\

\subsection { Atomic bomb}
- FDR died in April 12, 1945. Harry Truman, took office and used the atmoic bomb.\\
- Atomic bomb is the part of \textbf{Manhattan Project} a top secret program in which American scientist developed an atomic bomb during World War II.\\
- August 6, 1945 dropped a bomb in Hiroshima, 280,000 civilians, 40,000 soldiers, and 70,000 died immediately.\\

\subsection{ United Nations}
- created in 1944 in Dumbarton Oaks, near Washington D.C\\
- Along with six rotating members , the Council would have five permanet ones- Britain, China, France, the Soviet Union, and United States.\\
- In 1945, represenatives of 51 countries met in San francisco to adopt UN charter, which outlawed force or threat of forces as a means of settling international disputes.\\
\end{document}