%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{article}
\textwidth = 550pt
\setlength{\hoffset}{-1.5in}
\begin{document}
\title{Reading Assignment 6: page 576 to page 608}
\author{Huy Le}

\maketitle

\section{Main keypoints in the reading}
\begin{itemize}
\item Canal Zone.
\item Rosevelt's Interventions.
\item Wilson's Interventions.
\item Lusitania.
\item Zimmerman Telegraph.
\item The Fourteen point
\item Selective Service Act of May 1917
\item CPI
\item Nineteenth Amendment.
\item Espionage Act
\item Buck v. Bell
\item W.E.B. Dubois
\item Versailles Treaty in 1918
\item The Balfour Declaration 
\item League of nation

\end{itemize}


\section{Keypoints Explained}
\subsection{ Canal Zone}
- 1903, Columbia refuse to cede lane in Panama, Rosevelt helped to set in motion an uprising by Panamian conspirators\\
- Establish the independence , Panama singed a treaty giving the United States both the right to construct and operate a canal and sovereignty over the Canal Zone, a ten-mile wide strip of land through which the rout would run.\\
- Canal zone was the largest construction project in history up to that date. 60,000 workers, completed in 1914. It reduced the sea voyage between the East and West Coasts of the United States by 8,000 miles. \\

\subsection{Rosevelt's Interventions}
- Rosevelt Corollary to Monroe Doctrine: United States had the right to exercise ' an international police power in the Western Hermisphere'\\
- In 1904, Rosevelt ordered forces to seize the customs houses of the Dominician Republic to ensure payments of its debts to European and American Investor\\
- In 1906, Dispatched troops to Cuba to oversee a disrupted election; they remained in the country till 1909.
- Taff, landed marines to protect a goverment friendly to American economic interest. Taff emphasized the economic investment a loan than the military action, his foreign policy is called Dollar Diplomacy.\\

\subsection{Wilson's Intervention}
- Wilson promise that respecting the Latin's America Independence and free from economic domination but he couldn't abandon the idea that United States is responsible to teach other people the lessons of democracy.\\
- 1915, Sent marines to occupy Haiti after the goverment refuse to allow American banks to oversee its financial dealings. Left in 1934\\
- 1916, established a military goverment in Dominician Republic, with the US controlling the country's custom collections and paying its debts. The army left in 1924\\
- 1916, 'Pancho' Villa, the leader of one faction, attacked Collumbus, New Mexico, killed 17 Americans. Wilson ordered 10,000 troops into northern Mexico on an expedition that unsuccessfully sought to arrest Villa.\\

\subsection{Lusitania}
- May 1915, a German sumarines sank the British liner Lusitania causing the death of 1,198 passengers, including 124 Americans.\\
- The sinking of Lusitania ourraged American public opinions and strengthened the hand of those who believed that United States must prepare for possible entry into war.\\
- 1915, Wilson embarked on a policcy of 'Prepareness' - a crash program to expand the Amercan army and navy\\

\subsection{Zimmerman Telegraph}
- A message by Germanm foreign secretary Athur Zimmerman calling on Mexico to join in a cmoing war against the United States and promising to help it recover territory lost in Mexican War of 1846-1848.\\
- The telegraph played an important role to encourage Wilson to go before Congress to ask for a declaration of war against Germany.\\

\subsection{ The Fourteen points}
- Willson issued it in January 1918
- Key principles are 
\begin{itemize}
\item self determination for all nations.
\item freedom of the seas.
\item free trade
\item open dipmolacy
\item readjustment of colonial claims with colonized people given equal weight in deciding their futures.
\item creation of leuage of nations
\end{itemize}

\subsection{ Selective Service Act of May 1917}
- 24 millions men were required to register with the draft.\\

\subsection{CPI}
- Comittee on Public Information.\\
- Its purpose is to explain to American and the world the cause that compelled American to take arms in defense of its libertes and free institution.\\
- CPI appeals are in the progressive language of socical cooperation and expanded democracy.\\
- Abroad. means peace based on the principle of national self-determination.\\
- At home, means improving industrial democracy.\\
- CPI distributed pamphlets foreseeing a postwar society complete withe univeral 8 hours a day and a living wage for all\\

\subsection{Nineteenth Amendment.}
- Alice Paul: woman activist, got imprisomed for compared Wilson to Kaiser, and group of her followers chained themselves to the White Houses fence.\\
- The combination of women's patriotic service and widespread outrage over the treatment of Paul and her fellow prisoners pushed the administration toward full fledged support of woman suffrage.\\
- 1920, ratification of the Nineteenth Amendment, which barred states from using secx as a qualification for the suffrage.\\

\subsection{Espionage Act}
- Act of 1917 prohibited not only spying and interfering with the draft but also 'false statements' that might impede military success. \\
- It charged more than 2,000 people with violating these laws. \\
- Eugene V. Debs convicted in 1918  for delivering an antiwar speech. Deb's sentence was 10 years. He ran for president while still in prison in 1920 and recieved 900,000 votes. Debs got released in 1921.\\

\subsection{ Buck v. Bell}
- Indian in 1907 had passed a law authorizing doctors to sterilize insane and feeble-minded immates in mental institutions so that they wouldn't pass their 'defective' genes on to their children.\\
- 1927, the Supreme Court upheld the constitutionality of these laws. \\
- 1960s, 63,000 persons had been involuntarily sterilized.\\

\subsection{W.E.B. Dubois}
- Born in 1868, educated at Fisk and Havard.\\
- His career was the effort to reconcile the contradiction between what he called 'American Freedom for whites and the continuing subjection of Negroes.' \\
- 1905, Du Bois gathered a group of black leaders at Niagara Falls, and organized the Niagara movement which sought to reinvigorate the abolitionist tradition.\\
- 1909, joined a group with mostly white reformers shocked by a lynching in Springfield. Illinois. He created the NAACP(National Association for the Advancement of Colored People). The NAACP, as it was known, launched a long struggle for the enforcement of the Fourteenth and Fifthteenth Amendments.\\

\subsection{ Versailles Treaty in 1918}
- Negotiations between American, British, and French.\\
- Established the Leguage of Nations.\\
- Applied the principle of self-determmination to eastern Europe and redrew the map of that religion.\\
- Declaring German morally responsible for the war, and German had to pay between \$33 billions and \$56 billions which crippled the German economy.\\

\subsection{The Balfour Declaration }
 - was a letter from the United Kingdom's Foreign Secretary Arthur James Balfour
to Baron Rothschild (Walter Rothschild, 2nd Baron Rothschild), a leader of the British Jewish community, for transmission to the Zionist Federation of Great Britain and Ireland.
\subsection{League of Nations}
- United States never part of it.
- The League of Nations (abbreviated as LN in English, and SDN in its other
official languages) was an intergovernmental organization founded as a result of the Paris Peace Conference that ended the First World War. It was the first international organization whose principal mission was to maintain world peace.[1] Its primary goals, as stated in its Covenant, included preventing wars through collective security and disarmament, and settling international disputes through negotiation and arbitration.[2] Other issues in this and related treaties included labour conditions, just treatment of native inhabitants, human and drug trafficking, arms trade, global health, prisoners of war, and protection of minorities in Europe.[3] At its greatest extent from 28 September 1934 to 23 February 1935, it had 58 members.

\subsection{The agreement in the Versailee.}
\begin{itemize}
  \item Sykes-picot agreement
  \item McMahan-Hussein corresp
  \item Balfour Declaration
\end{itemize}

\end{document}
