%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{article}

\begin{document}
\author{Huy Le}
\title{History 201 Reading Assignment 7}
\maketitle
\section{Main keypoints to the reading}
\begin{itemize}
  \item Billy Sunday
  \item The Scopes trial
  \item The second Klan
  \item 1924 immigration act
  \item Race Policy
  \item Pluralism
  \item Halem's culture
  \item The Great Depression
  \item How Depression affect American lives.
  \item How President Hoover responded
  \item Hawley-Smoot Tariff
\end{itemize}

\section{Keypoints explained}
\subsection{Billy Sunday}
- Christian belief, fundamentalist. \\
- most flamboyant apostle was Billy Sunday.\\
- at talented professional baseball player who became a revivalist preacher.\\
- 1900 to 1930 Sunday drew huge crowd with a highly theatrical preaching style
and a message denoucing sins ranging from Darwinism to alcohol. \\
- Prohibition which fundamentalist strongly supported, succeeded in reducing the consumption of alcohol as well as public drunkenness and drink related diseases\\

\subsection{The Scopes trial}
- In Tennessee, the trial of John Scopes, he was arrested for violating a state law that prohibited the teaching of Charles Darwin theory of evolution.\\
- There was two definition of freedom in American in prior to this trial
\begin{itemize}
\item Fundamentalist Christians, strong in rual areas of the South and West.
\item American Civil Liberties Union, freedom meant above all the right to independent thought and individual self-expression. which is Scope defenders.
\end{itemize} 
- reowened labor lawyer Clarence Darrow defend Scopes.\\
- The highlight of the trial came when William Jennings Bryan came to stand as an expert witness of the Bible: Bryan revealed an almost complete ignorance of modern science and proved unable to respond effectively to Darrow's sarcastic questioning.\\
- The jury found Scopes guilty, although the Tennesse supreme court later overturned the decision on a technicality.\\

\subsection{The second Klan}
- reborn in Atlanta in 1915 after the lynching of Leo Frank, a jewish factory manager accused of kiling a teenage girl. \\
- American civilization The Klan insist, was endangered not only by blacks but by immigrants(especially Jews and Catholics) and all the forces(ferminism, unions, immorality, even , on ocasion the giant coporation) that endanger the individual liberty.\\
- Klan's influence faded after the 1925, when its leader in India was convicted of assaulting a young woman.\\

\subsection{1924 immigration act}
- 1921, restricted European immigration to 357,000 per year which is one-third of the annual average before the war.\\
- Three years later limited to 150,000 peryear. \\
- 1924, no limits on immigration from the Western Hemisphere.\\

\subsection{ Race Policy}
- President Cololidge singed the new law about race policy, immigration policy must now rest on a biological definition of the ideal population\\
- reflect the desire to improve the quality of democratic citizenship\\
- reveal how these aims were overlaid with pseudo scientific assumptions about the superior and inferior races.\\
- concept of race lacked of any rational foundation, and the Supreme Court agree to it in 1923, White was not a scientific concept at all but part of common speech to be interpreted with the understanding of common man.\\

\subsection {Pluralism}
- The idea of Pluralism came from the intepretation of the Supreme Court of the Fourteenth Amendment. It is the guarantee of equal liberty to include the right to marry establish a home and bring up children and to practice religion as one chose without the inteference from the state.

\subsection{Halem's culture}
- New York's Halem gained an international reputaion as the capital of black America.\\
- 1920, it became famous for slumming when whites visted dance halls, jazz clubs, search for exotic adventure. Harlem of the white imagination was a place of primitive passions, free from the puritanical restraints of mainstream American culture.\\
- Harlem Renaissance\\
\begin{itemize}
\item Harlem became the links to New York'artistic mainstream
\item Poets and Novelists such as Cullen, Hughes, and McKay were sponsored by white intellectuals and published by white presses.
\item New Negro become a term for black to ask for rejection of stereotype and asking for black values.
\item This quest of new negro and he emerge of Harlem have led to something call the Harlem Renaissance
\item Writing from Harlem Renaissance root for the black experience and contained the strong element of protest. they want to say that blacks would no longer allow themselves to be murdered defenselessly by whites.
\end{itemize}

\subsection{ The Great Depression}
- Black Tuesday, stock market crashed. As panic selling set in, more than \$10 billion in market value(equivalent to more than ten times now) vanished in five hours. U.S and entire world find itself in the grip of the Great Depression, the greatest economic desaster in mordern history.\\
- Before 1929, signs of economic trouble became evident. spectacular burst, banks failing, land remain underdeveloped, mortgage forceclosed. European demands for American goods reduced. \\
- German refused to pay debts made leading these goverment to stop paying debts to American.\\
- Bank failed because of the depositors withdrew money, Millions of families lost their life savings.\\
- 1929, the gross natinal product had fallen by one-third prices by nearly 40 percent, and more than 11 million Americans-25 percent of labor forces. could not find work.\\

\subsection{How Depression affect American lives.}
- Detroit, 4000 children stood in bread lines each day seeking food.\\
- In Chicago, where half of the working population can't find work at beginning of 1932.\\
- Soviet ask for workers, 100,000 applications from the United States.\\
- Many American return to rural area to grow their own food for their family. 1953, 33 millions people lived on farms.\\
- Suicide rate rose to the highest level in nation's history, brith rate fall to the lowest\\

\subsection{ How President Hoover responded}
- He didn't much, not really caring partly because of the advice from Adrew Mellon that economic downturn were a normal part of capitalism.\\
- He even said that the Government should not support the people because federal aid weakens the studiness of our national character.\\
- His responses were considered as associational action which means that he put his faith in voluntary steps by business to maintain investment and employment, and efforts by charity organizations to assist needy neighbors.\\
- He made a comment about unemployed men selling apple that Many persons left their jobs for more profitable one of selling apple. This makes me believe this guys is a horrible President.\\

\subsection{ Hawley-Smoot Tariff}
- 1930, made economic situation worse.\\
- Raising the already high taxes on imported goods, it inspired similar increase aboard, leading to reduce international trade.\\

\subsection {Differences between the fundamentalist and modernist}
- Fundamentalists intepret the text literally, disregard the changes in
society'sknowledge\\
 - Modernists intepret the text metaphorically, that accomondates science with
 their ideas. \\

\end{document}
